Titeln på avhandlingens språk

### 2022-11-02 background.tex
comments
Update on Overleaf.
neuroticism

    \item The above effects are modulated by the Big Five~\cite{oliver:bfi1999} trait of \emph{neuroticism}, as evidenced by a \ac{PCA}.
\end{enumerate}

In the following, we employ the above insights together with the actual data collected for~\cite{olguinmunoz:impact2021} to design and build a probabilistic model of human behavior for \ac{WCA}.

>>>>

    \item The above effects are modulated by an individual personality trait.
    We will discuss this in detail below in \cref{ssec:moderationeffects}
\end{enumerate}

\subsubsection{Moderation of effects by individual characteristics}\label{ssec:moderationeffects}

We recorded variables related to well-known individual differences, encompassing both the \acf{BFI}, introduced by \textcite{oliver:bfi1999}, and the \acf{ITQ}, described by \textcite{witmer1998measuring}.
Out of the collected individual-difference variables, the most salient one corresponded to \emph{neuroticism}, a \ac{BFI} trait linked to low tolerance for stress and high emotional reactivity, and which has previously been linked to higher \emph{delay discounting} rates~\cite{hirsh2008delay}.
Delay discounting is the tendency to devalue rewards for which one must wait; high rates, indicative of waiting intolerance, have been associated with negative social and academic outcomes.

\begin{figure}
    \centering
    \includegraphics[width=.9\columnwidth]{figs/new_model/correlation_neuro_exectime.png}
    \caption{%
        Correlation between neuroticism and the mean execution time of the last four steps in segments of \num{12} steps subject to the same \ac{TTF} in~\textcite{olguinmunoz:impact2021}.
        Pearson correlation coefficient \( \rho = 0.418 \), 2-tailed \( p < 0.05 \).
    }\label{fig:neuroexectimecorrel}
\end{figure}

Neuroticism was identified as a modulating factor for the pacing effects through a \ac{PCA}.
Out of the three identified components, which cumulatively accounted for \SI{73.13}{\percent} of the variance in the results, neuroticism was included in the first two.
The effect of neuroticism was transversal to all \acp{TTF} and impairment durations in the tasks --- we show an example of the correlation between execution time and neuroticism in \cref{fig:neuroexectimecorrel}

\begin{figure}
    \centering
    \includegraphics[width=.9\columnwidth]{figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \acs*{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \ac{TTF} in \textcite{olguinmunoz:impact2021}.
        Fits were performed using the \ac{MLE} method.
    }\label{fig:muexgaussian}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/new_model/dist_fits_neuro.png}
    \caption{%
        Example \ac{exGaussian} fits on execution times from steps \numrange{4}{8} in a segment of steps at the maximum experimental \ac{TTF}.
        The effects of neuroticism are clearly visible in the tail and the mean of the distributions.
    }\label{fig:fitsneuro}
\end{figure*}

Furthermore, we found that execution times, when grouping by experimental variables such as neuroticism, \ac{TTF}, and continuous segments of steps subject to the same \ac{TTF}, were well-fit by an \ac{exGaussian} distribution, as verified using Kolmogorov-Smirnov goodness-of-fit tests~\cite{massey1951kolmogorov}.
This distribution has an ample body of research supporting its suitability for the modeling of the timing of human actions and reaction times~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
We found that the effects of neuroticism on execution times were clearly identifiable in the fitted distributions, in particular in their means and tails.
\cref{fig:muexgaussian} shows an example of this modulating effect, illustrating the behavior of the mean (\( \mu \) parameter) of \ac{exGaussian} distributions fitted to the execution times of the first four steps of segments of steps subject to the same \ac{TTF}.
Finally, \cref{fig:fitsneuro} shows an example of the effects of neuroticism on the fitted \ac{exGaussian} distributions for a specific group of execution times.
Higher neuroticism directly translates into a higher mean and longer tail.

### 2022-11-02 model.tex
neuroticism

In the following subsections, we detail the construction of a model which uses the data collected for \textcite{olguinmunoz:impact2021} to generate, at runtime, realistic execution times. 
In order to accurately emulate the behavior of a human, such a model needs to implement two main behaviors.
One, it needs to generate realistic execution times for each step in the task, considering the current and historical impairment of the \ac{WCA} system.
We detail this in \cref{ssec:model:exectimes}.
And two, it needs to produce sequences of input samples for each step mimicking what a real human would generate; this is explained in \cref{ssec:model:frames}.
Finally, in \cref{ssec:model:obtaining} we briefly discuss where implementations of this model can be obtained.

>>>>

In the following, we employ the above insights together with the actual data collected for~\cite{olguinmunoz:impact2021} to design and build a probabilistic model of human behavior for \ac{WCA}.
We detail the construction of a model which uses the data collected to generate, at runtime, realistic execution times. 
In order to accurately emulate the behavior of a human, such a model needs to implement two main behaviors.
One, it needs to generate realistic execution times for each step in the task, considering the current and historical impairment of the \ac{WCA} system.
We detail this in \cref{ssec:model:exectimes}.
And two, it needs to produce sequences of input samples for each step mimicking what a real human would generate; this is explained in \cref{ssec:model:frames}.
Finally, in \cref{ssec:model:obtaining} we briefly discuss where implementations of this model can be obtained.
